### 2018-02-02 submission/manuscript.Rmd
update fig legends to select community

**Figure 4: Stool OTU Random Forest Model Across Studies.** A) Adenoma random forest model between the full community and select genera OTUs only. B) Carcinoma random forest model between the full community and select genera OTUs only. The dotted line represents an AUC of 0.5 and the lines represent the range in which the AUC for the 100 different 80/20 runs fell between. The solid red line represents the median AUC of all the studies for either the full community or select genera OTUS only model.

**Figure 5: Tissue OTU Random Forest Model Across Studies.** A) Adenoma random forest model between the full community and select genera OTUs only. B) Carcinoma random forest model between the full community and select genera OTUs only. The dotted line represents an AUC of 0.5 and the lines represent the range in which the AUC for the 100 different 80/20 runs fell between. The solid red line represents the median AUC of all the studies for either the full community or select genera OTUS only model.

>>>>

**Figure 4: Stool OTU Random Forest Model Across Studies.** A) Adenoma random forest model between the full and select community OTUs only. B) Carcinoma random forest model between the full and select community OTUs only. The dotted line represents an AUC of 0.5 and the lines represent the range in which the AUC for the 100 different 80/20 runs fell between. The solid red line represents the median AUC of all the studies for either the full or select community OTUS only model.

**Figure 5: Tissue OTU Random Forest Model Across Studies.** A) Adenoma random forest model between the full and select community OTUs only. B) Carcinoma random forest model between the full and select community OTUs only. The dotted line represents an AUC of 0.5 and the lines represent the range in which the AUC for the 100 different 80/20 runs fell between. The solid red line represents the median AUC of all the studies for either the full community or select genera OTUS only model.

### 2018-02-02 submission/manuscript.tex
update fig legends to select community

\textbf{Figure 4: Stool OTU Random Forest Model Across Studies.} A)
Adenoma random forest model between the full community and select genera
OTUs only. B) Carcinoma random forest model between the full community
and select genera OTUs only. The dotted line represents an AUC of 0.5
and the lines represent the range in which the AUC for the 100 different
80/20 runs fell between. The solid red line represents the median AUC of
all the studies for either the full community or select genera OTUS only
model.

\textbf{Figure 5: Tissue OTU Random Forest Model Across Studies.} A)
Adenoma random forest model between the full community and select genera
OTUs only. B) Carcinoma random forest model between the full community
and select genera OTUs only. The dotted line represents an AUC of 0.5
and the lines represent the range in which the AUC for the 100 different
80/20 runs fell between. The solid red line represents the median AUC of
all the studies for either the full community or select genera OTUS only
model.

>>>>

\textbf{Figure 4: Stool OTU Random Forest Model Across Studies.} A)
Adenoma random forest model between the full and select community OTUs
only. B) Carcinoma random forest model between the full and select
community OTUs only. The dotted line represents an AUC of 0.5 and the
lines represent the range in which the AUC for the 100 different 80/20
runs fell between. The solid red line represents the median AUC of all
the studies for either the full or select community OTUS only model.

\textbf{Figure 5: Tissue OTU Random Forest Model Across Studies.} A)
Adenoma random forest model between the full and select community OTUs
only. B) Carcinoma random forest model between the full and select
community OTUs only. The dotted line represents an AUC of 0.5 and the
lines represent the range in which the AUC for the 100 different 80/20
runs fell between. The solid red line represents the median AUC of all
the studies for either the full community or select genera OTUS only
model.
